PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$

### 2014-08-05 qfenv_paper/qf_environment.tex
Further edits and new envcount dist figure

In Section \ref{sec:primus} and Section \ref{sec:sdss} we provide a brief summary of the PRIMUS data and the SDSS data used for our sample selection. Then in Section \ref{sec:target} we define our stellar mass complete galaxy sample. Afterwards, in Section \ref{sec:sfq}, we classify our sample galaxies as quiescent or star-forming then calculate the environment using a volume-limited {\em Environment Defining Population} in Section \ref{sec:environment}. 
Finally in Section \ref{sec:edgeeffect}, we correct our galaxy sample and environment measurements for edge effects of the surveys.

\subsection{PRIMUS} \label{sec:primus}
At intermediate redshifts we use multiwavelength imaging and spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim 120,000$ precise spectroscopic redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range $z \approx 0-1.2$. The survey was conducted using a IMACS spectrograph on a Magellan I Baade $6.5$ m telescope with a slitmask and low dispersion prism. For details on the PRIMUS observation methods such as survey design, targeting, and data summary, we refer readers to the survey papers: \cite{Coil:2011aa} and \cite{Cool:2013aa}.

@@

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.2}
	\plotone{fig_edp_sdss_z005_012_primus_z02_10_Mr_redshift.png}
        \caption{Absolute magnitude $M_{r}$ versus redshift for the target galaxy population (black squares) with the Environment Defining Population (red circles) plotted on top. Both samples are divided into redshift bins:$z \approx 0.0375-0.145$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right). Stellar mass completeness limits are imposed on the target galaxy population (Section \ref{sec:target}) while the $M_{r}$ limits are imposed on the EDP (Section \ref{sec:environment}). The lowest redshift bin ($z \approx 0.0375-0.145$; leftmost panel) contain our galaxy sample and EDP selected from SDSS. The rest contain galaxies and EDP selected from PRIMUS.} \label{fig:targetEDP}
    \end{center}
\end{figure*}

\subsection{SDSS-GALEX} \label{sec:sdss}
At low redshifts, we use spectroscopic redshifts and high fidelity $ugriz$ photometry from the SDSS Data Release 7 (DR7; \cite{Abazajian:2009aa}). More specifically we select galaxies from the New York University Value-Added Galaxy Catalog (hereafter SDSS VAGC) that satisfy the main sample criterion and have galaxy extinction corrected Petrosian magnitudes $14.5 < r < 17.6$ and spectroscopic redshifts within $0.01 < z < 0.2$ (\cite{Blanton:2005aa}). We further restrict the SDSS VAGC sample to only galaxies with medium depth observations with total exposure time greater than $1 \; \rm{ks}$ from {\em GALEX} Release 6. This leaves $167,727$ galaxies.

@@

In order to quantify the effects of these photometric underestimations in our analysis, we replace our SDSS fluxes in the $ugriz$ band with $ugriz$ fluxes from the NASA-Sloan Atlas (NSA) catalog, which incorporate the improved background subtraction presented in \cite{Blanton:2011aa} and uses single-Seric fit fluxes rather than the standard SDSS \texttt{cmodel} fluxes. Using the ratio of the luminosity derived from the improved photometry over the luminosity derived from the standard SDSS VAGC photometry, we impose a preliminary correction on the stellar mass values obtained from \texttt{iSEDfit} assuming a consistent mass-to-light ratio. This mass correction leads to a significant increase in the stellar mass function for $\mathcal{M} > 10^{11} \mathcal{M}_{\odot}$ that matches the results from \cite{Bernardi:2013aa}. However, the effect of the mass correction was negligible for the quiescent fraction evolution results. As a result, we do not discuss the issues with photometric measurements any further in this paper. The effects of the discussed photometry methods on the luminosity function and stellar mass function will be examined in detail in future work.

\subsection{Galaxy Sample} \label{sec:target} 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig_envcount_cylr2h25_thresh75_sdss_z0_05_0_12_primuszerr_masslimit_histogram.png,height=0.5\textwidth}
     \caption{Environment measure distribution for our galaxy sample.}      \label{fig:envcount}
    \end{center}
\end{figure*}
From the low redshift SDSS-{\em GALEX} and intermediate redshift PRIMUS data, in this section, we define our mass complete galaxy sample. We begin by imposing the parent sample selection criteria from \cite{Moustakas:2013aa}. More specifically, we take the statistically complete {\em primary} sample from the PRIMUS data (\cite{Coil:2011aa}) and impose magnitude limits on optical selection bands as specified in \cite{Moustakas:2013aa} Table 1. These limits are in different optical selection bands and have distinct values for the five PRIMUS target fields. We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$). Lastly, we impose a redshift range of $ 0.2 < z < 0.8$ for the PRIMUS galaxy sample, where $ z > 0.2$ is selected due to limitations from sample variance and $ z < 0.8$ is selected due to the lack of sufficient statistics in subsamples defined below.

@@

We present the absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) in Figure \ref{fig:targetEDP}. The left-most panel corresponds to the sample derived from the SDSS-{\em GALEX} data and the rest correspond to the target sample derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$.

\subsection{Classifying Quiescent and Star-Forming Galaxies} \label{sec:sfq}
We now classify our mass complete galaxy sample into quiescent or star-forming using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa} Section 3.2. This classification method utilizes the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming galaxies observed at least until $z \sim 2$ (\cite{Noeske:2007aa}). The PRIMUS sample displays a well-defined SF sequence within the redshift range of our galaxy sample. Then using the power-law slope for the SF sequence from \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \cite{Moustakas:2013aa}):
\begin{equation}
\rm{log}(\rm{SFR}_{\rm{min}}) = -0.49 + 0.64 \rm{log}(\mathcal{M} - 10) +1.07(z-0.1), 
\end{equation} \label{eq:qsfclass} 
where $\mathcal{M}$ is the stellar mass of the galaxy. If the target galaxy SFR and stellar mass lies above Equation \ref{eq:qsfclass} we classify it as star-forming; if below, as quiescent (\cite{Moustakas:2013aa} Figure 1.).

\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lit_2envbin_primuszerr.eps,height=0.75\textwidth,angle=90}
     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) target galaxies in 
low (left) and high (right) environments from redshift range $z=0-0.8$. The environment of each galaxy  
was calculated using a cylindrical aperture size of $R=2 \: \rm{Mpc}$ and $H=25 \: \rm{Mpc}$ and  
classification based on the cut-offs specified in Table \ref{tab:aperture}. The SMFs use mass bins of 
width $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.25$. In each panel we use shades of blue 
(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
progressively lighter.}      \label{fig:smf}
    \end{center}
\end{figure*}

\subsection{Galaxy Environment} \label{sec:environment}
We define the environment of a galaxy as the number of neighboring {\em Environment Defining Population} galaxies (defined below) within a fixed aperture centered around it. We use a fixed aperture measurement of environment because, as \cite{Muldrew:2012aa} finds in their comparison of different environment definition using simulations, it provides a better probe of the entire halo in comparison to other definitions of environment such as nearest neighbor, which provides a better tracer at inter-halo scales.

@@

The analysis we describe below uses a fixed cylindrical aperture with dimensions $R_{\rm{ap}} = 2 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25 \: \rm{Mpc}$ to measure environment. The same analysis was extended for varying aperture dimensions $R_{\rm{ap}} = 1, 2, 3 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25, 50 \: \rm{Mpc}$. We also adjusted the environment classification thresholds for these analyses. The results obtained from using different apertures and environment classification thresholds are consistent with the results later presented.  
\begin{figure*}
    \begin{center}
        \leavevmode
        \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lit_primuszerr.eps,height=0.75\textwidth,angle=90}
        \caption{Evolution of the quiescent fraction $f_{\rm{Q}}$ for galaxies in low (left) and high (rights) density environments for $z < 0.8$. $f_{\rm{Q}}$s were calculated using the SMFs in Figure\ref{fig:smf}, as described in text. Darker shading indicates lower redshift.}         \label{fig:qf}
    \end{center}
\end{figure*}

\subsection{Edge Effects} \label{sec:edgeeffect}
One of the challenges in obtaining accurate galaxy environments using a fixed aperture method is accounting for the edges of the survey. For galaxies located near the edge of the survey, part of the fixed aperture encompassing it will lie outside the survey regions. In this case, $n_{env}$ only reflects the fraction of the environment within the survey geometry.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%% CONTINUE EDITING!%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
To account for these edge effects, we use a Monte Carlo method to impose edge cutoffs on our galaxy sample. We begin by computing the angular separation, $\theta_{\rm{ap}}$ that corresponds to the radius of the fixed aperture (used to measure environment) at the redshifts of the galaxies. Then we compute the environment, $n_{\rm{ransack}}$, of our galaxy sample with the EDP replaced by a \texttt{ransack} sample of $N_{\rm{ransack}} = 1,000,000$ points with $RA$ and $Dec$ randomly selected within the window function of the EDP. We compare the $n_{\rm{ransack}}$ values to the expected value computed based on the angular area of the environment defining aperture and the EDP window function: 
\begin{equation} \label{eq:ransack}
E[n_{\rm{ransack}}] = \frac{N_{\rm{ransack}}}{A_{\rm{EDP}}}\times {\pi \theta_{\rm{ap}}^2} \times f_{\rm{thresh}}. 
\end{equation} 
$A_{\rm{EDP}}$ is the total angular area of the EDP window function and $f_{\rm{thresh}}$ is the fractional threshold for the edge effect cut-off, which we vary based on $R_{\rm{ap}}$ (listed in Table \ref{tab:aperture}). If $n_{\rm{ransack}}$ for a target galaxy is greater than $E[n_{\rm{ransack}}]$ then the galaxy remains in our sample; otherwise, it is discarded.

\section{Stellar Mass Function} \label{sec:smf}
The target galaxy sample defined above has so far been classified into quiescent or star-forming and low or high density environments. We further divide these subsamples into redshift bins: $0.0375-0.145$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ for a total 16 subsamples. In this section, we calculate the SMF for each of these subsamples.

To calculate the SMFs we employ a non-parametric $1/{V_{\rm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}. The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\rm{max,avail},i}}. 
\end{equation}
The equation above is same as Equation 3. in \cite{Moustakas:2013aa} except that we use $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}. $w_i$ is the statistical weight of galaxy $i$ and $\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ is the number of galaxies ($N$) per unit volume within the stellar mass range $[\rm{log} \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log} \:\mathcal{M})]$.

@@

To calculate $V_{\rm{max,avail},i}$, we generate a sample of points with random $RA$, $Dec$ within the window function of our galaxy sample (SDSS-{\em GALEX} window function and the five PRIMUS fields) and random $z$ within the redshift range. This is not to be confused with the \texttt{ransack} sample in Section \ref{sec:edgeeffect}. We then impose the same edge effect cutoffs we applied to our galaxy sample, using the same \texttt{ransack} environment calculation method, also discuseed in Section \ref{sec:edgeeffect}. At redshift bins of $\Delta z \sim 0.01$, we compute the fraction of random points that remain in the bin after the edge effect cutoffs: $f_{\rm{edge}}$. We then apply this factor to compute $V_{\rm{max,avail}} = V_{\rm{max}} \times f_{\rm{edge}}$. The $V_{\rm{max}}$ in the equation above are computed following the method described in \cite{Moustakas:2013aa} Section 4.2 with the same redshift-dependent $K$-correction from observed SED and luminosity evolution model.

In order to calculate the uncertainty of the SMFs from the sample variance, we use a standard jackknife technique (as done in \cite{Moustakas:2013aa}). For the PRIMUS galaxies, we calculate SMFs after excluding one of the five target fields at a time. For the SDSS target galaxies we divide the field into a 12 $\times$ 9 rectangular $RA$ and $Dec$ grid and calculate the SMFs after excluding one grid each time. Using the calculated SMFs we calculate the uncertainty: 
\begin{equation}
\sigma^j = \sqrt{\frac{M-1}{M} \sum\limits_{k=1}^{M} (\Phi^j_k - \langle \Phi^j \rangle)^2}
\end{equation} 
$M$ in this equation is the number of jack knife SMFs in the stellar mass bin. $\langle \Phi^j \rangle$ is the mean number density of galaxies 
in each stellar mass bin for all of the jack knife $\Phi^j$s.

In Figure \ref{fig:smf}, we present the SMFs for 16 target galaxy subsamples classified into quiescent/star-forming (orange/blue, bottom/top panels) and high/low environment density (left/right panels). The redshift evolution of the SMFs in each of these panels are indicated by a darker shade for lower redshift bins. The sample variance uncertainties are illustrated through the width of the SMFs.

>>>>

In Section \ref{sec:primus} and Section \ref{sec:sdss} we provide a brief summary of the PRIMUS data and the SDSS data used for our sample selection. Then in Section \ref{sec:target} we define our stellar mass complete galaxy sample. Afterwards, in Section \ref{sec:sfq}, we classify our sample galaxies as quiescent or star-forming then calculate the environment using a volume-limited {\em Environment Defining Population} in Section \ref{sec:environment}. 
Finally in Section \ref{sec:edgeeffect}, we correct our galaxy sample and environment measurements for edge effects of the surveys. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PRIMUS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PRIMUS} \label{sec:primus}
At intermediate redshifts we use multiwavelength imaging and spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim 120,000$ precise spectroscopic redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range $z \approx 0-1.2$. The survey was conducted using a IMACS spectrograph on a Magellan I Baade $6.5$ m telescope with a slitmask and low dispersion prism. For details on the PRIMUS observation methods such as survey design, targeting, and data summary, we refer readers to the survey papers: \cite{Coil:2011aa} and \cite{Cool:2013aa}.

@@

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.2}
	\plotone{fig_edp_sdss_z005_012_primus_z02_10_Mr_redshift.png}
        \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top. Both samples are divided into redshift bins:$z \approx 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right). The lowest redshift bin ($z \approx 0.05-0.12$; leftmost panel) contain our galaxy sample and EDP selected from SDSS. The rest contain galaxies and EDP selected from PRIMUS. The redshift limits for the lowest redshift bin are empirically selected based on the bright and faint limits of SDSS galaxies. Stellar mass completeness limits, specified in Section \ref{sec:target}, are imposed on the galaxy population. Meanwhile, $M_{r}$ limits are applied to the EDP such that the number density in each panel are equivalent (Section \ref{sec:environment}).} \label{fig:targetEDP}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SDSS-GALEX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{SDSS-GALEX} \label{sec:sdss}
At low redshifts, we use spectroscopic redshifts and high fidelity $ugriz$ photometry from the SDSS Data Release 7 (DR7; \cite{Abazajian:2009aa}). More specifically we select galaxies from the New York University Value-Added Galaxy Catalog (hereafter SDSS VAGC) that satisfy the main sample criterion and have galaxy extinction corrected Petrosian magnitudes $14.5 < r < 17.6$ and spectroscopic redshifts within $0.01 < z < 0.2$ (\cite{Blanton:2005aa}). We further restrict the SDSS VAGC sample to only galaxies with medium depth observations with total exposure time greater than $1 \; \rm{ks}$ from {\em GALEX} Release 6. This leaves $167,727$ galaxies.

@@

In order to quantify the effects of these photometric underestimations in our analysis, we replace our SDSS fluxes in the $ugriz$ band with $ugriz$ fluxes from the NASA-Sloan Atlas (NSA) catalog, which incorporate the improved background subtraction presented in \cite{Blanton:2011aa} and uses single-Seric fit fluxes rather than the standard SDSS \texttt{cmodel} fluxes. Using the ratio of the luminosity derived from the improved photometry over the luminosity derived from the standard SDSS VAGC photometry, we impose a preliminary correction on the stellar mass values obtained from \texttt{iSEDfit} assuming a consistent mass-to-light ratio. This mass correction leads to a significant increase in the stellar mass function for $\mathcal{M} > 10^{11} \mathcal{M}_{\odot}$ that matches the results from \cite{Bernardi:2013aa}. However, the effect of the mass correction was negligible for the quiescent fraction evolution results. As a result, we do not discuss the issues with photometric measurements any further in this paper. The effects of the discussed photometry methods on the luminosity function and stellar mass function will be examined in detail in future work. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GALAXY SAMPLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Galaxy Sample} \label{sec:target} 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig_envcount_cylr2h25_thresh75_sdss_z0_05_0_12_primuszerr_masslimit_histogram.png,height=0.5\textwidth}
     \caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample. The star-forming galaxies contribution to the distribution is colored blue and diagonally patterned. The contribution of the distribution from quiescent galaxies is colored in red. Each redshift panel is divided into three sections of by the environment classification threshold (vertical black lines): low density environment $n_{\rm{env}} < 1.5$ and high density environment $n_{\rm{env}} > 3.5$. The percentages of the redshift bin contained in the environment classifications are presented above the distribution. For example at $0.2 < z < 0.4$, $56.0 \%$ of galaxies in the redshift bin have low density environments while $29.0\%$ of galaxies in the redshift bin have high density environments. }      \label{fig:envcount}
    \end{center}
\end{figure*}

From the low redshift SDSS-{\em GALEX} and intermediate redshift PRIMUS data, in this section, we define our mass complete galaxy sample. We begin by imposing the parent sample selection criteria from \cite{Moustakas:2013aa}. More specifically, we take the statistically complete {\em primary} sample from the PRIMUS data (\cite{Coil:2011aa}) and impose magnitude limits on optical selection bands as specified in \cite{Moustakas:2013aa} Table 1. These limits are in different optical selection bands and have distinct values for the five PRIMUS target fields. We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$). Lastly, we impose a redshift range of $ 0.2 < z < 0.8$ for the PRIMUS galaxy sample, where $ z > 0.2$ is selected due to limitations from sample variance and $ z < 0.8$ is selected due to the lack of sufficient statistics in subsamples defined below.

@@

We present the absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) in Figure \ref{fig:targetEDP}. The left-most panel corresponds to the sample derived from the SDSS-{\em GALEX} data and the rest correspond to the target sample derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CLASSIFYING QUIESCENT AND STAR-FORMING GALAXIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Classifying Quiescent and Star-Forming Galaxies} \label{sec:sfq}
We now classify our mass complete galaxy sample into quiescent or star-forming using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa} Section 3.2. This classification method utilizes the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming galaxies observed at least until $z \sim 2$ (\cite{Noeske:2007aa}). The PRIMUS sample displays a well-defined SF sequence within the redshift range of our galaxy sample. Then using the power-law slope for the SF sequence from \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \cite{Moustakas:2013aa}):
\begin{equation}
\rm{log}(\rm{SFR}_{\rm{min}}) = -0.49 + 0.64 \rm{log}(\mathcal{M} - 10) +1.07(z-0.1), 
\end{equation} \label{eq:qsfclass} 
where $\mathcal{M}$ is the stellar mass of the galaxy. If the target galaxy SFR and stellar mass lies above Equation \ref{eq:qsfclass} we classify it as star-forming; if below, as quiescent (\cite{Moustakas:2013aa} Figure 1.).

\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lit_2envbin_primuszerr.eps,height=0.75\textwidth,angle=90}
     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) target galaxies in 
low (left) and high (right) environments from redshift range $z=0-0.8$. The environment of each galaxy  
was calculated using a cylindrical aperture size of $R=2 \: \rm{Mpc}$ and $H=25 \: \rm{Mpc}$ and  
classification based on the cut-offs specified in Table \ref{tab:aperture}. The SMFs use mass bins of 
width $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.25$. In each panel we use shades of blue 
(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
progressively lighter.}      \label{fig:smf}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GALAXY ENVIRONMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Galaxy Environment} \label{sec:environment}
We define the environment of a galaxy as the number of neighboring {\em Environment Defining Population} galaxies (defined below) within a fixed aperture centered around it. We use a fixed aperture measurement of environment because, as \cite{Muldrew:2012aa} finds in their comparison of different environment definition using simulations, it provides a better probe of the entire halo in comparison to other definitions of environment such as nearest neighbor, which provides a better tracer at inter-halo scales.

@@

The analysis we describe below uses a fixed cylindrical aperture with dimensions $R_{\rm{ap}} = 2 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25 \: \rm{Mpc}$ to measure environment. The same analysis was extended for varying aperture dimensions $R_{\rm{ap}} = 1, 2, 3 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25, 50 \: \rm{Mpc}$. We also adjusted the environment classification thresholds for these analyses. The results obtained from using different apertures and environment classification thresholds are consistent with the results later presented.  
\begin{figure*}
    \begin{center}
        \leavevmode
        \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lit_primuszerr.eps,height=0.75\textwidth,angle=90}
        \caption{Evolution of the quiescent fraction $f_{\rm{Q}}$ for galaxies in low (left) and high (rights) density environments for $z < 0.8$. $f_{\rm{Q}}$s were calculated using the SMFs in Figure\ref{fig:smf}, as described in text. Darker shading indicates lower redshift.}         \label{fig:qf}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDGE EFFECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Edge Effects} \label{sec:edgeeffect}
One of the challenges in obtaining accurate galaxy environments using a fixed aperture method is accounting for the edges of the survey. For galaxies located near the edge of the survey, part of the fixed aperture encompassing it will lie outside the survey regions. In this case, $n_{env}$ only reflects the fraction of the environment within the survey geometry.

To account for these edge effects, we use a Monte Carlo method to impose edge cutoffs on our galaxy sample. We first construct a \texttt{ransack} sample of  $N_{\rm{ransack}} = 1,000,000$ points with $RA$ and $Dec$ randomly selected within the window function of the EDP (so SDSS EDP and PRIMUS EDP separately). We then compute the angular separation, $\theta_{i, \rm{ap}}$ that corresponds to $R_{\rm{ap}}$ (Section \ref{sec:environment}) at the redshift of each sample galaxy $i$. For each sample galaxy we count the number of \texttt{ransack} points within $\theta_{i, \rm{ap}}$ of the galaxy: $n_{i,\rm{ransack}}$. Afterwards, we compare $n_{i,\rm{ransack}}$ to the expected value computed from the angular area of the environment defining aperture and the EDP window function: 
\begin{equation} \label{eq:ransack}
E_{i}[n_{\rm{ransack}}] = \frac{N_{\rm{ransack}}}{A_{\rm{EDP}}}\times {\pi \theta_{i, \rm{ap}}^2} \times f_{\rm{thresh}}. 
\end{equation} 
$A_{\rm{EDP}}$ is the total angular area of the EDP window function and $f_{\rm{thresh}}$ is the fractional threshold for the edge effect cut-off. For $R_{\rm{ap}}= 2\;\rm{Mpc}$, $f_{\rm{thresh}} = 0.75$. If $n_{i, \rm{ransack}} > E_{i}[n_{\rm{ransack}}]$ then galaxy $i$ remains in our sample; otherwise, it is discarded.

Once the edge effect cuts are applied, we are left with the final galaxy sample. In Figure \ref{fig:envcount} we present the distribution of environment measurements ($n_{\rm{env}}$) for our final galaxy sample in redshift bins: $0.05 - 0.12$, $0.2 - 0.4$, $0.4-0.6$, and $0.6-0.8$. The quiescent galaxy contributions are colored in red while the star-forming galaxy contributions are colored in blue and patterned. The low and high density environment classifications are represented by black vertical lines that divide the distribution at $n_{\rm{env}} = 1.5$ and $n_{\rm{env}} = 3.5$. The percentage of the total galaxies in the redshift bin that are in these environment densities are labeled on the figure.

Although we imposed PRIMUS redshift errors on our SDSS galaxies in order to consistently measure environment throughout our entire sample, we note a significant discrepancy between the SDSS and PRIMUS samples in the fractional contribution of each environment classification within the redshift bin. For each of the PRIMUS redshift bins, approximately $50 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $38 \%$ of galaxies in the redshift bin are in low density environments and $45 \%$ are in high density environments. We remind the reader that this is due to the different mass-completeness limits imposed on our galaxy sample for each redshift bins. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Stellar Mass Function} \label{sec:smf}
Our galaxy sample has so far been classified into quiescent or star-forming and low or high density environments. We further divide these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ for a total 16 subsamples. In this section, we calculate the SMF for each of these subsamples.

To calculate the SMFs we employ a non-parametric $1/{V_{\rm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}. The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\rm{max,avail},i}}. 
\end{equation}
$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ is the number of galaxies ($N$) per unit volume within the stellar mass range $[\rm{log} \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log} \:\mathcal{M})]$. The equation above is same as Equation 3. in \cite{Moustakas:2013aa} except that we use $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.

@@

To calculate $V_{\rm{max,avail},i}$, we use a similar Monte Carlo method as the edge effect cutoffs in Section \ref{sec:edgeeffect}. First, we generate a sample of points with random $RA$, $Dec$ within the window function of our galaxy sample (SDSS-{\em GALEX} window function and the five PRIMUS fields) and random $z$ within the redshift range. These points are not to be confused with the \texttt{ransack} sample in Section \ref{sec:edgeeffect}. We apply the edge effect cutoffs on these random points as we did for our galaxy sample using the same \texttt{ransack} method in Section \ref{sec:edgeeffect}. At redshift bins of $\Delta z \sim 0.01$, we calculate the fraction of the random points that remain in the bin after the edge effect cutoffs over the total number of random points in the bin: $f_{\rm{edge}}$. We then apply this factor to compute $V_{\rm{max,avail}} = V_{\rm{max}} \times f_{\rm{edge}}$. The $V_{\rm{max}}$ in the equation above are computed following the method described in \cite{Moustakas:2013aa} Section 4.2 with the same redshift-dependent $K$-correction from observed SED and luminosity evolution model.

To calculate the uncertainty of the SMFs from the sample variance, we use a standard jackknife technique (as done in \cite{Moustakas:2013aa}). For the PRIMUS galaxies, we calculate SMFs after excluding one of the five target fields at a time. For the SDSS target galaxies we divide the field into a 12 $\times$ 9 rectangular $RA$ and $Dec$ grid and calculate the SMFs after excluding one grid at a time. From the calculated SMFs we calculate the uncertainty: 
\begin{equation}
\sigma^j = \sqrt{\frac{M-1}{M} \sum\limits_{k=1}^{M} (\Phi^j_k - \langle \Phi^j \rangle)^2}
\end{equation} 
$M$ in this equation is the number of jack knife SMFs in the stellar mass bin. $\langle \Phi^j \rangle$ is the mean number density of galaxies in each stellar mass bin for all of the jack knife $\Phi^j$s.

In Figure \ref{fig:smf}, we present the SMFs of the quiescent/star-forming (orange/blue, bottom/top panels) and high/low density environment (left/right panels) subsamples. The redshift evolution of the SMFs in each of these panels are indicated by a darker shade for lower redshift bins. The width of the SMFs represent the sample variance uncertainties.

As a result, we caution that the SMF redshift evolution is inconsistent during the transition from the PRIMUS sample to the SDSS sample at $z \sim 0.2$.
